MSAD_PCA_Walkthrough

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
pkgdown doesn't like the path in .Rbuildignore, so switch "\" to "/" and it works. Also, I added a thesis paragraph, and labelled all the sections.

@@

\section{Simulating Data with \texttt{mspProcessData}}
This function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations. We follow the seminal work of \cite{dong_batch_1996} for generation of the foundational stationary and independent features.

@@

\section{Training with \texttt{mspTrain}}

@@

\section{Monitor and Issue Alarms with \texttt{mspMonitor} and \texttt{mspWarning}}

@@

\section{Example Simulation Workflow}

This section provides a fully commented code walk-through for the main \texttt{msp*} functions in the \texttt{mvMonitoring} package. This package depends on a few other packages, but most of these dependencies are on commonly-used packages. The exception is \texttt{BMS}.
<<r load_mvMonitoring>>=
library(devtools)
library(xts)
# install.packages("BMS") # If necessary
build("C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring")
library(mvMonitoring)
@

@@

\subsection{Warn Operators During Alarms}
Note that all `Alarm` codes in the monitor matrix above are recorded with \texttt{NA} values. This is because the \texttt{mspMonitor} function does not check the sequential flag conditions of the monitor matrix. This is the responsibility of the \texttt{mspWarning} function. Because the \texttt{mspWarning} function is designed to test one incoming observation at a time through a script or batch file, the following example is designed to mimic the behavior of the \texttt{mspWarning} function as each new observation comes online.
<<r warnings>>=
alarm1A_xts <- monitor1A_xts
for(i in 1:nrow(alarm1A_xts)){
  if(i < (5 + 1)){
    alarm1A_xts[1:i,] <- mspWarning(alarm1A_xts[1:i,])
  }else{
    alarm1A_xts[(i - 5):i,] <- mspWarning(alarm1A_xts[(i - 5):i,])
  }
}
@
The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
<<r warning_Plot>>=
plot(alarm1A_xts[, ncol(alarm1A_xts)],
     main = "Alarm Codes for Test Data")
@
The alarm codes are
\begin{enumerate}
\item ``0'': No alarm.
\item ``1'': Hotelling's $T^2$ alarm.
\item ``2'': Squared Prediction Error alarm.
\item ``3'': Both alarms.
\end{enumerate}
As we can see, the monitoring function detects a process anomaly after 40 minutes into the test hour, and the warning function issues the corresponding alarms.
% Package Implementation in Practice
% Kathryn B. Newhart will send me a brief discussion of how she has implemented this package in wastewater treatment monitoring at a facility in Golden, CO.

>>>>

We outline this vignette as follows. In Section \ref{sec:D_Motivation}, we discuss the motivation for creating this package, and briefly explain the utility of multi-state process monitoring. In Section \ref{sec:D_DataGen}, we offer a thorough explination of how to generate the synthetic data we employed to test and compare the new multi-state modification of the process monitoring setup with the \texttt{mspProcessData} function. In Section \ref{sec:D_Train}, we describe the necessary information and data formatting to effectively train the fault detection algorithm using the \texttt{mspTrain} function. Then, in Section \ref{sec:D_Alarms}, we list and explain the necessary inputs to the \texttt{mspMonitor} and \texttt{mspWarning} functions and examine their outputs. Section \ref{sec:D_Workflow} shows a step-by-step walkthrough of how to implement the four \texttt{mvMonitoring} functions in practice. We offer some concluding remarks in Section \ref{sec:D_Conclusion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  Motivation  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Motivation} \label{sec:D_Motivation}

@@

\section{Simulating Data with \texttt{mspProcessData}} \ref{sec:D_DataGen}
This function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations. We follow the seminal work of \cite{dong_batch_1996} for generation of the foundational stationary and independent features.

@@

\section{Training with \texttt{mspTrain}} \label{sec:D_Train}

@@

\section{Monitor and Issue Alarms with \texttt{mspMonitor} and \texttt{mspWarning}} \label{sec:D_Alarms}

@@

\section{Example Simulation Workflow} \label{sec:D_Workflow}

This section provides a fully commented code walk-through for the main \texttt{msp*} functions in the \texttt{mvMonitoring} package. This package depends on a few other packages, but most of these dependencies are on commonly-used packages. The exception is \texttt{BMS}.
<<r load_mvMonitoring, warning=FALSE, message=FALSE>>=
library(devtools)
library(xts)
# install.packages("BMS") # If necessary
build("C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring")
library(mvMonitoring)
@

@@

\subsection{Warn Operators During Alarms}
Note that all `Alarm` codes in the monitor matrix above are recorded with \texttt{NA} values. This is because the \texttt{mspMonitor} function does not check the sequential flag conditions of the monitor matrix. This is the responsibility of the \texttt{mspWarning} function. Because the \texttt{mspWarning} function is designed to test one incoming observation at a time through a script or batch file, the following example is designed to mimic the behavior of the \texttt{mspWarning} function as each new observation comes online.
<<r warnings>>=
alarm1A_xts <- monitor1A_xts
for(i in 1:nrow(alarm1A_xts)){
  if(i < (5 + 1)){
    alarm1A_xts[1:i,] <- mspWarning(alarm1A_xts[1:i,])
  }else{
    alarm1A_xts[(i - 5):i,] <- mspWarning(alarm1A_xts[(i - 5):i,])
  }
}
@
The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
<<r warning_Plot>>=
plot(alarm1A_xts[, ncol(alarm1A_xts)],
     main = "Alarm Codes for Test Data")
@
The alarm codes are
\begin{enumerate}
\item ``0'': No alarm.
\item ``1'': Hotelling's $T^2$ alarm.
\item ``2'': Squared Prediction Error alarm.
\item ``3'': Both alarms.
\end{enumerate}
As we can see, the monitoring function detects a process anomaly after 40 minutes into the test hour, and the warning function issues the corresponding alarms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  Conclusion  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion} \label{sec:D_Conclusion}
We have supplied our motivation for this package, and we have discussed implementing a multivariate process monitoring scheme with this package using the example of a decentralized WWT plant in Golden, CO. We believe that this software will provide system engineers with the tools necessary to quickly and accurately detect abnormalities in multivariate, autocorrelated, non-stationary, non-linear, and multi-state water treatment systems. Further, we have given a synthetic example showing how the functions within this package would be implemented and tuned in practice.

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
pkgdown doesn't like the path in .Rbuildignore, so switch "\" to "/" and it works. Also, I added a thesis paragraph, and labelled all the sections.

\section{Example Simulation Workflow}

This section provides a fully commented code walk-through for the main \texttt{msp*} functions in the \texttt{mvMonitoring} package. This package depends on a few other packages, but most of these dependencies are on commonly-used packages. The exception is \texttt{BMS}.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(devtools)}
\end{alltt}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: package 'devtools' was built under R version 3.4.1}}\begin{alltt}
\hlkwd{library}\hlstd{(xts)}
\end{alltt}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: package 'xts' was built under R version 3.4.1}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required package: zoo}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# \\\#\# Attaching package: 'zoo'}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# The following objects are masked from 'package:base':\\\#\# \\\#\#\ \ \ \  as.Date, as.Date.numeric}}\begin{alltt}
\hlcom{# install.packages("BMS") # If necessary}
\hlkwd{build}\hlstd{(}\hlstr{"C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# "{}C:/PROGRA\textasciitilde{}1/R/R-34\textasciitilde{}1.0/bin/x64/R"{} --no-site-file --no-environ --no-save\ \ \textbackslash{}\\\#\#\ \  --no-restore --quiet CMD build\ \ \textbackslash{}\\\#\#\ \  "{}C:\textbackslash{}Users\textbackslash{}gabriel\_odom\textbackslash{}Documents\textbackslash{}GitHub\textbackslash{}mvMonitoring\textbackslash{}mvMonitoring"{}\ \ \textbackslash{}\\\#\#\ \  --no-resave-data --no-manual}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# }}\begin{verbatim}
## [1] "C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring_0.1.0.tar.gz"
\end{verbatim}
\begin{alltt}
\hlkwd{library}\hlstd{(mvMonitoring)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

##   Data: num [1:4142, 1:5] 0.364 0.425 0.821 1.004 0.864 ...

@@

##   .. ..$ SPE_threshold   : Named num 4.7

@@

##   .. ..$ T2_threshold    : Named num 59.7

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.424 -0.384 0.437 0.433 -0.308 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.206 0 0 1.513
##   .. ..$ muTrain         : Named num [1:6] 1.38 -2.09 2.96 1.37 -2.05 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.54 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 1.35

@@

##   .. ..$ T2_threshold    : Named num 76.8

@@

##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4995 -0.0334 0.4931 -0.5255 -0.1688 ...
##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.285 0 0 0 0.72 ...
##   .. ..$ muTrain         : Named num [1:6] 2.977 -0.566 -4.498 2.951 -0.591 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.07 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 5.85

@@

##   .. ..$ T2_threshold    : Named num 80.7

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.396 0.454 0.454 -0.153 0.461 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.276 0 0 0.499
##   .. ..$ muTrain         : Named num [1:6] 0.528 0.272 1.44 0.568 0.258 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.4 0 0 0 0 ...

@@

\subsubsection{Adding Lagged Features}
First, concatenate the last given observation from the training set as ``row 0'' of the test data set. This will enable \texttt{mspMonitor} to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{test1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{8460}\hlopt{:}\hlnum{8520}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{]}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{lag.xts}\hlstd{(test1A_xts,} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{)}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{cbind}\hlstd{(fault1A_xts[}\hlnum{8461}\hlopt{:}\hlnum{8520}\hlstd{,}\hlnum{1}\hlstd{],}
                       \hlstd{lagTest1A_xts[}\hlopt{-}\hlnum{1}\hlstd{,])}
\hlkwd{head}\hlstd{(lagTest1A_xts)}
\end{alltt}
\begin{verbatim}
##                     state         x         y        z       x.1
## 2015-05-22 07:00:00     1 0.7465717 -1.582803 1.141042 0.3817970
## 2015-05-22 07:01:00     1 0.8064225 -1.564885 1.226738 0.7465717
## 2015-05-22 07:02:00     1 0.7621322 -1.603962 1.150504 0.8064225
## 2015-05-22 07:03:00     1 0.7995411 -1.785750 1.149927 0.7621322
## 2015-05-22 07:04:00     1 0.8638972 -1.822695 1.116856 0.7995411
## 2015-05-22 07:05:00     1 0.7735952 -1.505855 1.139623 0.8638972
##                            y.1       z.1
## 2015-05-22 07:00:00  0.1052954 0.3582939
## 2015-05-22 07:01:00 -1.5828027 1.1410421
## 2015-05-22 07:02:00 -1.5648852 1.2267384
## 2015-05-22 07:03:00 -1.6039621 1.1505043
## 2015-05-22 07:04:00 -1.7857497 1.1499272
## 2015-05-22 07:05:00 -1.8226952 1.1168557
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsubsection{Monitoring the Test Data}
With the lagged test observations in the working environment, the \texttt{mspMonitor} function can be applied. This function (similarly to \texttt{mspTrain}) takes in the label information as a separate argument from the input data. Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}. Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{monitor1A_xts} \hlkwb{<-} \hlkwd{mspMonitor}\hlstd{(}\hlkwc{observations} \hlstd{= lagTest1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
                            \hlkwc{labelVector} \hlstd{= lagTest1A_xts[,}\hlnum{1}\hlstd{],}
                            \hlkwc{trainingSummary} \hlstd{= train1A_ls}\hlopt{$}\hlstd{TrainingSpecs)}
\hlkwd{head}\hlstd{(monitor1A_xts)}
\end{alltt}
\begin{verbatim}
##                             x         y        z       x.1        y.1
## 2015-05-22 07:00:00 0.7465717 -1.582803 1.141042 0.3817970  0.1052954
## 2015-05-22 07:01:00 0.8064225 -1.564885 1.226738 0.7465717 -1.5828027
## 2015-05-22 07:02:00 0.7621322 -1.603962 1.150504 0.8064225 -1.5648852
## 2015-05-22 07:03:00 0.7995411 -1.785750 1.149927 0.7621322 -1.6039621
## 2015-05-22 07:04:00 0.8638972 -1.822695 1.116856 0.7995411 -1.7857497
## 2015-05-22 07:05:00 0.7735952 -1.505855 1.139623 0.8638972 -1.8226952
##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
## 2015-05-22 07:00:00 0.3582939 0.3441627        0 29.445080       0    NA
## 2015-05-22 07:01:00 1.1410421 0.3811468        0  3.329163       0    NA
## 2015-05-22 07:02:00 1.2267384 0.2937754        0  3.222249       0    NA
## 2015-05-22 07:03:00 1.1505043 0.1424375        0  2.810259       0    NA
## 2015-05-22 07:04:00 1.1499272 0.2947956        0  2.630555       0    NA
## 2015-05-22 07:05:00 1.1168557 0.8742699        0  3.708552       0    NA
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\end{knitrout}
The alarm codes are
\begin{enumerate}
\item ``0'': No alarm.
\item ``1'': Hotelling's $T^2$ alarm.
\item ``2'': Squared Prediction Error alarm.
\item ``3'': Both alarms.
\end{enumerate}
As we can see, the monitoring function detects a process anomaly after 40 minutes into the test hour, and the warning function issues the corresponding alarms.
% Package Implementation in Practice
% Kathryn B. Newhart will send me a brief discussion of how she has implemented this package in wastewater treatment monitoring at a facility in Golden, CO.

>>>>

\section{Example Simulation Workflow} \label{sec:D_Workflow}

This section provides a fully commented code walk-through for the main \texttt{msp*} functions in the \texttt{mvMonitoring} package. This package depends on a few other packages, but most of these dependencies are on commonly-used packages. The exception is \texttt{BMS}.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(devtools)}
\hlkwd{library}\hlstd{(xts)}
\hlcom{# install.packages("BMS") # If necessary}
\hlkwd{build}\hlstd{(}\hlstr{"C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## [1] "C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring_0.1.1.tar.gz"
\end{verbatim}
\begin{alltt}
\hlkwd{library}\hlstd{(mvMonitoring)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

##   Data: num [1:4142, 1:5] 1.062 0.186 0.364 0.335 0.383 ...

@@

##   .. ..$ SPE_threshold   : Named num 4.61

@@

##   .. ..$ T2_threshold    : Named num 59.6

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.425 -0.378 0.439 0.434 -0.305 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.208 0 0 1.482
##   .. ..$ muTrain         : Named num [1:6] 1.39 -2.09 2.99 1.38 -2.05 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.55 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 1.4

@@

##   .. ..$ T2_threshold    : Named num 74.6

@@

##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4962 -0.0673 0.4888 -0.5234 -0.187 ...
##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.284 0 0 0 0.732 ...
##   .. ..$ muTrain         : Named num [1:6] 3.003 -0.564 -4.526 2.977 -0.589 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.08 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 6.51

@@

##   .. ..$ T2_threshold    : Named num 83.4

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.393 -0.452 -0.455 0.157 -0.464 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.274 0 0 0.507
##   .. ..$ muTrain         : Named num [1:6] 0.527 0.273 1.434 0.567 0.259 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.6 0 0 0 0 ...

@@

\subsubsection{Adding Lagged Features}
First, concatenate the last given observation from the training set as ``row 0'' of the test data set. This will enable \texttt{mspMonitor} to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{test1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{8460}\hlopt{:}\hlnum{8520}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{]}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{lag.xts}\hlstd{(test1A_xts,} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{)}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{cbind}\hlstd{(fault1A_xts[}\hlnum{8461}\hlopt{:}\hlnum{8520}\hlstd{,}\hlnum{1}\hlstd{],}
                       \hlstd{lagTest1A_xts[}\hlopt{-}\hlnum{1}\hlstd{,])}
\hlkwd{head}\hlstd{(lagTest1A_xts)}
\end{alltt}
\begin{verbatim}
##                     state         x         y         z       x.1
## 2015-05-22 07:00:00     1 0.5894923 -1.693457 0.9793838 0.4122657
## 2015-05-22 07:01:00     1 0.7076477 -1.693444 1.1569904 0.5894923
## 2015-05-22 07:02:00     1 0.6065543 -1.510750 1.0816650 0.7076477
## 2015-05-22 07:03:00     1 0.5964738 -1.404200 0.9984129 0.6065543
## 2015-05-22 07:04:00     1 0.7359302 -1.492578 0.9049884 0.5964738
## 2015-05-22 07:05:00     1 0.7665503 -1.482806 0.9188497 0.7359302
##                            y.1       z.1
## 2015-05-22 07:00:00  0.1370214 0.4769939
## 2015-05-22 07:01:00 -1.6934574 0.9793838
## 2015-05-22 07:02:00 -1.6934436 1.1569904
## 2015-05-22 07:03:00 -1.5107499 1.0816650
## 2015-05-22 07:04:00 -1.4042005 0.9984129
## 2015-05-22 07:05:00 -1.4925779 0.9049884
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsubsection{Monitoring the Test Data}
With the lagged test observations in the working environment, the \texttt{mspMonitor} function can be applied. This function (similarly to \texttt{mspTrain}) takes in the label information as a separate argument from the input data. Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}. Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{monitor1A_xts} \hlkwb{<-} \hlkwd{mspMonitor}\hlstd{(}\hlkwc{observations} \hlstd{= lagTest1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
                            \hlkwc{labelVector} \hlstd{= lagTest1A_xts[,}\hlnum{1}\hlstd{],}
                            \hlkwc{trainingSummary} \hlstd{= train1A_ls}\hlopt{$}\hlstd{TrainingSpecs)}
\hlkwd{head}\hlstd{(monitor1A_xts)}
\end{alltt}
\begin{verbatim}
##                             x         y         z       x.1        y.1
## 2015-05-22 07:00:00 0.5894923 -1.693457 0.9793838 0.4122657  0.1370214
## 2015-05-22 07:01:00 0.7076477 -1.693444 1.1569904 0.5894923 -1.6934574
## 2015-05-22 07:02:00 0.6065543 -1.510750 1.0816650 0.7076477 -1.6934436
## 2015-05-22 07:03:00 0.5964738 -1.404200 0.9984129 0.6065543 -1.5107499
## 2015-05-22 07:04:00 0.7359302 -1.492578 0.9049884 0.5964738 -1.4042005
## 2015-05-22 07:05:00 0.7665503 -1.482806 0.9188497 0.7359302 -1.4925779
##                           z.1        SPE SPE_Flag        T2 T2_Flag Alarm
## 2015-05-22 07:00:00 0.4769939 1.23315168        0 28.293817       0    NA
## 2015-05-22 07:01:00 0.9793838 0.06691071        0  3.842885       0    NA
## 2015-05-22 07:02:00 1.1569904 0.43929620        0  4.405378       0    NA
## 2015-05-22 07:03:00 1.0816650 0.86684372        0  5.023986       0    NA
## 2015-05-22 07:04:00 0.9984129 0.45658085        0  4.864228       0    NA
## 2015-05-22 07:05:00 0.9049884 0.74949850        0  4.396364       0    NA
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\end{knitrout}
The alarm codes are
\begin{enumerate}
\item ``0'': No alarm.
\item ``1'': Hotelling's $T^2$ alarm.
\item ``2'': Squared Prediction Error alarm.
\item ``3'': Both alarms.
\end{enumerate}
As we can see, the monitoring function detects a process anomaly after 40 minutes into the test hour, and the warning function issues the corresponding alarms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  Conclusion  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion} \label{sec:D_Conclusion}
We have supplied our motivation for this package, and we have discussed implementing a multivariate process monitoring scheme with this package using the example of a decentralized WWT plant in Golden, CO. We believe that this software will provide system engineers with the tools necessary to quickly and accurately detect abnormalities in multivariate, autocorrelated, non-stationary, non-linear, and multi-state water treatment systems. Further, we have given a synthetic example showing how the functions within this package would be implemented and tuned in practice.
